---
title: "ANLY 512 DataViz Project"
author:
- "Akpany Benjamin Ebby"
- "Lyne Melina Ignanga"
- "Anantha"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
references:
- id: munzner2015
  title: Visualization Analysis and Design (AK Peters Visualization Series)
  author:
  - family: Munzner
    given: Tamara
  publisher:  CRC Press Kindle Edition
  page: 97
  type: book
  isbn: 9781498759717
  issued:
    year: 2015
---

---

#### Document as of `r Sys.Date()`

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY512_DataVizProject_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(kableExtra)
read_chunk('R/ANLY512_DataVizProject_Chunks.R')

```

Some helper functions do exists to support the code snippets below such as: ```fullFilePath```

---

# DataViz Project

---

Let's start by installing the __*[Required Libraries]*__, then load them, and proceed to __*[Loading the Data Sheets]*__.

```{r installLibraries, echo=FALSE, eval=FALSE}
```

```{r loadLibraries, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r loadData, echo=FALSE, message=FALSE, warning=FALSE}
```

## Conclusion

Our analysis refererred to concepts from [see @munzner2015].

---

# Appendix:

### Required Libraries

```{r installLibraries, eval=FALSE}
```

```{r loadLibraries, eval=FALSE}
```

### Helper Functions

```{r helperFunctions, eval=FALSE}
```

### Loading the Data

```{r loadData, eval=FALSE}
```

---

## References
