---
title: "ANLY 512 DataViz Final Project Plan"
author:
- "Akpany Benjamin Ebby"
- "Lyne Melina Ignanga"
- "Anantha"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    highlight: zenburn
comment: Rmd Document with Markdown + Embedded R Code
references:
- id: munzner2015
  title: Visualization Analysis and Design (AK Peters Visualization Series)
  author:
  - family: Munzner
    given: Tamara
  publisher: CRC Press Kindle Edition
  page: 97
  type: book
  isbn: "9781498759717"
  issued:
  year: 2015
- id: sustainable_transport2015
  title: Sustainable Urban Transport
  author:
  - family: Attard
    given: Maria
  - family: Shiftan
    given: Yoram
  - family: Ison
    given: Stephen
  - family: Shaw
    given: Jon
  publisher: Emerald Publishing Limited
  type: book
  isbn: "9781784416157"
  issued:
  year: 2015
- id: weather_resilience2013
  title: Weather and Climate Resilience - Effective Preparedness through National Meteorological and Hydrological Services
  author:
  - family: Rogers
    given: David P.
  - family: Tsirkunov
    given: Vladimir V.
  - family: Tsirkunov
    given: Vladimir
  publisher: World Bank Publications
  type: book
  isbn: "9781464800276"
  issued:
  year: 2013
---

```{r setup, include=FALSE, purl=FALSE, eval=TRUE}

source('R/ANLY512_DataVizProject_Helper.R')

```

```{r echo=FALSE}

library(knitr)
library(kableExtra)
read_chunk('R/ANLY512_DataVizProject_Chunks.R')

```

---

# DataViz Project Plan

## Overview of Project.

For this project, we will analyze and visualize the effects of both the weather and holidays patterns on public transportation in New York City.
In particular, we will bring our focus on how those factors impact the rides or pick ups of [Uber](https://www.uber.com/) as well as [Taxi Cabs](http://www.yellowcabnyctaxi.com/).
 
# Issues Related to Focus.
As part of our analysis, we will leverage some existing literature on the subjects of public transportation, weather resilience, and Data Visualiztion
[see @weather_resilience2013 @sustainable_transport2015 @munzner2015].

## Data Sources.

We found the following [Kaggle](https://www.kaggle.com/) datasets very interesting for our project:
* [NYC Uber Pickups with Weather and Holidays](https://www.kaggle.com/yannisp/uber-pickups-enriched/home) Subset of Uber pickup data with weather, borough, and holidays
* [New York City Taxi Trip - Hourly Weather Data](https://www.kaggle.com/meinertsen/new-york-city-taxi-trip-hourly-weather-data) Improve Machine Learning with more detailed weather data

```{r loadLibraries, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r loadUberTaxiData}
```


## Current Analysis Strategy.

For our Analysis, we will make two hypothesis that we will attempt to verify:
* The weather does influence Uber Rides in New York City
* The weather does influence Taxi Pickups Rides in New York City
* Holidays do influence Taxi Pickups Rides in New York City
* Holidays do influence Taxi Pickups Rides in New York City
* The combination weather and Holidays do influence Taxi Pickups Rides in New York City
* The combination weather and Holidays do influence Taxi Pickups Rides in New York City

The use of data visualizations or DataVis [@munzner2015] will guide us on where to look as to which factors in the data
we should focus on. Indeed, graphics such as: *heatmaps*, *density plots*, *ridgeline plots*, *histograms*, *boxplots*
may come in very handy [@munzner2015].

## Summary of Time Investment of Each Team Member.

The contribution of our team members will be as follows:

__Benjamin:__
- github repository
- analysis
- graphics
- R scripts

__Lyne:__
- group communication
- analysis
- graphics
- R scripts

__Anantha:__
- publications and references
- analysis
- graphics
- R scripts

# bibliography.
